Embedded Domain Specific Languages inside Functional Languages

### 2014-03-13 paper.tex
Starting monadic reification

There are two fundimental types of Domain Specific Languages
(Figure X).
%
The first, like the SQL example, is a first class language,
with its own compiler or interpreter, and is often used in
its own ecosystem. (Figure X, (1)) 
All the examples mentioned so far fall
into this categary. The primary difference between SQL and
(say) Java is one of scope and focus, though sometimes
DSLs grow to be as large are general purpose languages.
%
The other class of Domain Specific Languages are languages
embeeded inside another hosting language. Such languages
can have the look and feel of being their own languages,
but leaverage the host language to provide an exisiting
ecostructure and initial semantics. It is this second
class of DSLs we are interested in, and is the subject of
this paper.

@@

toSeq :: a -> Signal a
toSeq = ...
\end{Code}

@@

The obvious questions are does this trick used here scale,
and what are the limitations? The trick has
been used on may large examples, including
generating large telemerty circuits, 
and (( .. feldspar )). It is considered a
stardard pattern in the functional programming
community, analogoues to the OO patterns
enumerated in the gang of four book~\cite{..}.
The trick is made all the more appealing
because we can use operator overloading.
But the trick does has serious limitations.

The basis of a Deep EDSL is one of constructiveness.
The aim is to construct a structure, then
use that structure that was previously implicit.
Figure sumurizes the state of the art with
deeply embeeded reification

>>>>

There are two fundamental types of Domain Specific Languages
(Figure X).
%
The first, like the SQL example, is a first class language,
with its own compiler or interpreter, and is often used in
its own ecosystem. (Figure X, (1)) 
All the examples mentioned so far fall
into this categary. The primary difference between SQL and
(say) Java is one of scope and focus, though sometimes
DSLs grow to be as large are general purpose languages.
%
The other class of Domain Specific Languages are languages
embedded inside another hosting language. Such languages
can have the look and feel of being their own languages,
but leverage the host language to provide an existing
eco-structure and initial semantics. It is this second
class of DSLs we are interested in, and is the subject of
this paper.

@@

toSeq :: a -> Signal a
toSeq = ...

instance Signal Sig where {...}

\subsection{How to spot an imperative}

Sometimes, a list of actions is the best way to express what you want to do.
In Haskell, the \verb|do|-notation is used to chain together imperative actions.
To give an example,

@@

The obvious questions are do this tricks used here scale,
and what are the limitations? The trick has
been used on may large examples, including
generating large telemerty circuits, 
and (( .. feldspar )). It is considered a
stardard pattern in the functional programming
community, analogoues to the OO patterns
enumerated in the gang of four book~\cite{..}.
The trick is made all the more appealing
because we can use operator overloading.
But the trick does has serious limitations.

The basis of a Deep EDSL is one of constructiveness.
The aim is to construct a structure, then
use that structure that was previously implicit.
Figure summarizes the state of the art with
deeply embedded reification
